Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-12 paper/structureScene.tex
Edit objects section

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of an object-based representation of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934},  we consider in this paper a quantization scheme that is as generic as possible, implemented using a clustering approach where coherent regions of the scene are identified. The clustering is done using the centroid-based $k$-means clustering algorithm.

Given a set of $d$-dimensional feature vectors $x_l^u\in X_u$, $l=\lbrace 1,2,\ldots,L\rbrace$, extracted from the scene $s_u$, $u=\lbrace 1,2,\ldots,U\rbrace$, the goal of $k$-means is to partition $X_u$ into $M$ clusters $c^u_m\in C_u$, $m=\lbrace 1,2,\ldots,M\rbrace$. The partitioning is done by minimizing for each cluster the squared error between its empirical mean (centroid) and the contained points. Given $\mu_m^u$ the centroid of the cluster $c_m^u$, $k$-means attempts to minimize the following objective function:
\begin{equation}
J(C_u)=\sum\limits_{m} \sum_{x^u_l\in c^u_m} \Vert x_l^u - \mu_m^u \Vert^2\mbox{.}
\end{equation}
Each scene $s_u$ is then described by a set of clusters $C_u$. One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, where the scene features are projected in a dictionary learned from the entire dataset.

@@

The similarity between all the scene centroids $\mu_i$, $i=\lbrace1,2,\ldots,I \rbrace$ with $I=UM$, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{ij} = \exp\left( - \dfrac{\Vert \mu_i - \mu_j \Vert^2}{\Vert \mu_i - \mu_{k,i} \Vert \Vert \mu_j - \mu_{k,j} \Vert} \right) 
\end{equation} 
where $\mu_{k,i}$ and $\mu_{k,j}$ are the $k^{\textrm{th}}$ nearest neighbor to the centroids $\mu_i$ and $\mu_j$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:
\begin{itemize}
\item \emph{ob-closest} (ob-c): the similarity between two scenes is equal to the largest similarity between their centroids,
\item \emph{ob-averaged} (ob-a): the similarity between two scenes is equal to the average of their centroid similarities, and
\item \emph{ob-weighted} (ob-w): for each scene, each centroid is weighted according to the number of frames belonging to its cluster. Each scene $s_u$ is thus described by a signature $p_u$ of $M$ clusters ($p_u=\lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace$), with $\mu_m^u$ and $w_m^u$ being the centroid and the weight of the $m$th cluster respectively. The similarity between scenes is then given by a cross-bin histogram distance, taking into account both the cluster weights and the distances between their centroids.
\end{itemize}

For \emph{ob-w}, the cross-bin histogram distance used is a variant of the earth mover's distance ($\EMD$), known as $\widehat{\EMD}$ and introduced in \cite{pele2008linear}. The $\EMD$ computes the distance between two histograms by finding the minimal cost to be paid to transform one histogram into the other. An advantage of $\EMD$ is that it automatically aligns the histogram bins by using a ``ground distance'' which is the distance between the bin centers in the two histograms. In our case, the histograms are the clusters weights $w^u$ defined over the bins formed by clusters centroids $\mu^u$.

The $\widehat{\EMD}$ variant of $\EMD$ is adapted for non-normalized histograms. To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $p_u$ and $p_v$ made of $n$ and $m$ clusters respectively, the $\widehat{\EMD}$ is computed by solving the following linear program:
\begin{equation}
\begin{split}
\widehat{\EMD}(p_u,p_v) &=\left( \min\limits_{\lbrace f_{nm}\rbrace} \sum\limits_{n,m} f_{nm}D_{nm}^{uv} \right) \\
&+ \left|\sum\limits_{n} w_n^u - \sum\limits_{m} w_m^v  \right| \alpha \max\limits_{n,m}\lbrace  D_{nm}^{uv}\rbrace.
\end{split}
\end{equation}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=\boldsymbol{1}-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$, respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

>>>>

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of object-based representations of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a quantization scheme that is as generic as possible, implemented using a clustering approach where coherent regions of the scene are identified. \ja{This last sentence is a bit hard to parse. Are we segmenting the time-series and identifying coherent regions?}

Given a set of $d$-dimensional feature vectors $X_u = \{x_1^u, \ldots, x_L^u\}$, extracted from the scene $s_u$, where $u=\lbrace 1,2,\ldots,U\rbrace$, we would like to partition $X_u$ into a set $C_u = \{c^u_1, \ldots, c^u_M\}$ of $M$ clusters. The partitioning is done by minimizing squared error between the empirical mean, or centroid, of each cluster and the vectors belonging to it. Letting $\mu_m^u$ denote the centroid of the cluster $c_m^u$, we attempt to minimize the following objective function:
\begin{equation}
J(C_u)=\sum\limits_{m} \sum_{x^u_l\in c^u_m} \Vert x_l^u - \mu_m^u \Vert^2\mbox{.}
\end{equation}
This is known as $k$-means clustering.
Each scene $s_u$ is then described by a set of clusters $C_u$. One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, where the scene features are projected in a dictionary learned from the entire dataset.

@@

The similarity between the scene centroids $\mu_i$ in the entire dataset, where $i=\lbrace1,2,\ldots,I \rbrace$ for $I=U \times M$, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{ij} = \exp\left( - \dfrac{\Vert \mu_i - \mu_j \Vert^2}{\Vert \mu_i - \mu_{k,i} \Vert \Vert \mu_j - \mu_{k,j} \Vert} \right).
\end{equation} 
Here, $\mu_{k,i}$ and $\mu_{k,j}$ are the $k^{\textrm{th}}$ nearest neighbor to the centroids $\mu_i$ and $\mu_j$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm. \ja{Wouldn't it be clearer to define $K$ using scene indices $u$ and $v$ and feature indices $m$ and $n$?}

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:
\begin{itemize}
\item \emph{ob-closest} (\emph{ob-c}): the similarity between two scenes is equal to the largest similarity between their centroids,
\item \emph{ob-averaged} (\emph{ob-a}): the similarity between two scenes is equal to the average of their centroid similarities, and
\item \emph{ob-weighted} (\emph{ob-w}): the similarity between two scenes is computed using a variant of the earth mover's distance applied to the set of centroids weighted by the number of frames assigned to its cluster.
\end{itemize}

For \emph{ob-w}, each centroid is weighted according to the number of frames belonging to its cluster. Each scene $s_u$ is thus described by a signature $p_u$ of $M$ clusters, where $p_u=\lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace$) and $\mu_m^u$ and $w_m^u$ are the centroid and the weight of the $m$th cluster, respectively. The similarity between scenes is then given by a cross-bin histogram distance known as the non-normalized earth mover's distance ($\widehat{\EMD}$) introduced by \cite{pele2008linear}. The $\widehat{\EMD}$ computes the distance between two histograms by finding the minimal cost for transforming one histogram into the other, where cost is measured by the number of transported histogram counts times the ``ground distance'' moved in terms of the histogram bins. In our case, the histogram counts are the clusters weights $w_m^u$ defined over the bins formed by the centroids $\mu_m^u$, so the ground distance is the distance over these cluster centroids.

To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $p_u$ and $p_v$, the $\widehat{\EMD}$ is computed by solving the following linear program:
\begin{equation}
\begin{split}
\widehat{\EMD}(p_u,p_v) &=\left( \min\limits_{\lbrace f_{nm}\rbrace} \sum\limits_{n,m} f_{nm}D_{nm}^{uv} \right) \\
&+ \left|\sum\limits_{n} w_n^u - \sum\limits_{m} w_m^v  \right| \alpha \max\limits_{n,m}\lbrace  D_{nm}^{uv}\rbrace.
\end{split}
\end{equation}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin, and $\alpha$ is a parameter which trades off between \ja{?}. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=\boldsymbol{1}-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$, respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.
